Tracing the Stellar Halos of Massive Galaxies to 100 kpc at $0.3<z<0.5$ using Hyper Suprime-Cam

### 2017-06-07 draft/paper1_v11.tex
Updated abstract

\begin{abstract} Massive galaxies display extended light profiles that can reach out to several hundreds of kiloparsecs. These extended stellar halos are key fossil records of the assembly history of massive galaxies.  Using data that is both wide (${\sim}100$ deg$^2$) and deep ($>28.5$ \sb{} in the $i$-band), we  present a systematic study of the stellar halos of the most massive galaxies (\mstar{}$\geq 11.5$) using a statistically significant sample of more than $7000$ galaxies at $0.3 < z < 0.5$. Our  study is based on high-quality (0.6\asec seeing) imaging data from the Hyper Suprime-Cam (HSC) survey which reaches ${\sim}4$ magnitudes fainter than SDSS and  enables us to directly trace mass profiles to 100 kpc without resorting to stacking. Shallow images and/or over-simplified models like \texttt{CModel} cannot capture the extended stellar halo and result in underestimated stellar masses. We show that this has a signifcant impact on  the high mass end of the galaxy mass function. The surface mass density profiles of massive galaxies are not self-similar; at fixed "core mass" they display a diverse  range of outer profiles. Galaxies in our sample have optical color gradients that are independent of galaxy mass but stellar halo ellipticites that increases with galaxy mass. Our results are broadly consistent with the two phase formation scenario of massive galaxies in which outer envelopes are built up at late times from minor merging. We provide surface mass surface mass density profiles in a convenient tabulated format to facilitate comparisons with predictions from numerical simulations of galaxy formation.\end{abstract}

>>>>

\begin{abstract}

    Massive galaxies display extended light profiles that can reach out to several 
    hundreds of kilo parsecs. 
    These extended stellar halos are key fossil records of the assembly history of 
    massive galaxies.  
    Using data that is both wide (${\sim}100$ deg$^2$) and deep ($>28.5$ \sb{} in 
    the $i$-band), we present a systematic study of the stellar halos of the most 
    massive galaxies (\mstar{}$\geq 11.5$) using a statistically significant sample 
    of more than $7000$ galaxies at $0.3 < z < 0.5$. 
    Our study is based on high-quality (0.6\asec seeing) imaging data from the Hyper 
    Suprime-Cam (HSC) survey which reaches ${\sim}4$ magnitudes fainter than SDSS in 
    surface brightness and enables us to directly trace mass profiles to 100 kpc 
    without resorting to stacking. 
    Shallow images and/or over-simplified models like \texttt{CModel} cannot capture 
    the extended stellar halo and result in underestimated stellar masses. 
    Our extended profiles reveal a number of mass-dependent trends. 
    We find that the halos of massive galaxies have higher ellipticity, and that the 
    outer ellipticity increases with stellar mass, but we find no evidence for trend 
    between stellar mass and color gradients. 
    As in previous work, we see a clear trend towards more extended outer profiles in 
    more massive galaxies. 
    Thus, when this extended light is not properly accounted for, the stellar mass 
    function is systematically underestimated at the highest masses. 
    Our results are broadly consistent with the two-phase formation scenario of 
    massive galaxies in which outer envelopes are built up at late times from series
    of mergers. 
    We provide surface mass density profiles in a convenient tabulated format to 
    facilitate comparisons with predictions from numerical simulations of galaxy 
    formation.

\end{abstract}
